\documentclass[10pt,letterpaper]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[scale=0.7,margin=0.5in]{geometry}
\usepackage{lmodern}

\name{Renjie}{Zhou}
\email{rzhou10@gmail.com}
\phone[mobile]{609-933-0310}
\address{}{Hoboken, NJ, 07030}
\homepage{https://rzhou10.github.io}
\social[linkedin]{rzhou10}
\social[github]{rzhou10}

\vspace*{-15mm}

\begin{document}

\makecvtitle

%change width of \cventry year
\sethintscolumntowidth{mmm yyyy -- mmm y}

\section{Work Experience}

\cventry{Sept 2022 - Oct 2023}{Software Engineer}{Shoppable\textregistered}{New York, NY}{}{
    \begin{itemize}
        \item Redesigned the dashboard in \textbf{React.js}/\textbf{CSS}/\textbf{Node.js}, reducing data widgets by about 10\% to reduce clutter.
        \item Refactored internal endpoints in \textbf{Node.js} to allow them to also be public facing, resulting in customers being able to fetch product information on the fly
        \item Redesigned the Ad Experience to use \textbf{Handlebars}/\textbf{CSS} to reduce load times by about 90\% and to integrate the DTC checkout experience
        \item Created a Rest API in \textbf{Node.js} to allow users to programmatically conduct checkouts resultig in greater flexibility in integrating with Shoppable
        \item Refactored all \textbf{React.js} projects to dynamically handle different localizations, allowing expansion into non English markets
\end{itemize}}
\cventry{Jul 2021 - Sept 2022}{Junior Software Engineer}{Shoppable\textregistered}{New York, NY}{}{
    \begin{itemize}
        \item Created builders for DTC and InstantShop with \textbf{React.js}/\textbf{CSS}/\textbf{Node.js}/\textbf{MongoDB}, resulting in users being able to save their customization for the cart and shop layouts.
        \item Created an interface \textbf{React.js}/\textbf{CSS}/\textbf{Node.js}/\textbf{MongoDB}, resulting in users being able to customized details about specific products
        \item Refactored the code base for DTC to follow better \textbf{React.js} practices, reducing the code base by about 15\% and improving performance by about 20\%
        \item Designed and built an admin interface in \textbf{React.js}/\textbf{CSS}/\textbf{Node.js}/\textbf{MongoDB}, resulting in internal employees easily managing information about merchants and customers
\end{itemize}}

\cventry{Jul 2019 - Jun 2021}{Software Developer}{Sphere Technology Solutions}{Hoboken, NJ}{}{
    \begin{itemize}
        \item Fixed UI bugs on Sphereboard in \textbf{Vue.js} to fix broken functionality, and changed \textbf{SQL} stored procedure logic to return accurate information.
        \item Added new features in \textbf{Vue.js}/\textbf{ASP.NET}/\textbf{SQL Server} to improve usability, such as the violation work table and the suspected admin finder.
        \item Modified the Connectors and Ingestor in \textbf{C\#} to collect/process additional information about files and folders, and to improve stability.
\end{itemize}
}
\cventry{Jun 2018 - Aug 2018}{Intern}{MedAZ.net}{West Windsor, NJ}{}{
    \begin{itemize}
        \item Built Rest APIs in \textbf{C\#} to dynamically retrieve and update website data.
        \item Utilized OATH authentication to allow password-less login via external services such as Facebook or Google.
        \item Sped up \textbf{SQL Server} access by replacing the previous Entity Framework with the faster Dapper ORM library.
\end{itemize}}

\cventry{Jul 2017 - Aug 2017}{Developer Intern}{MedAZ.net}{Princeton Junction, NJ}{}{
    \begin{itemize}
        \item Refactored the MaiEDEN web app to improve user accessibility and usability.
        \item Changed the color and position of buttons.
        \item Added functionalities such as a contact form, and a new service page.
\end{itemize}}

\section{Education}
\cventry{Aug 2014 - May 2019}{Bachelor of Engineering; Computer Engineering}{Stevens Institute of Technology}{Hoboken, NJ}{}{}

\section{Projects}
\cvitem{\href{https://github.com/chloequinto/SSW_555_Project}{\textbf{GEDCOM (genealogical data) parser}}}{
    A \textbf{Python} GEDCOM file parser to display information about a family tree, such as living people, and catch errors, such as incorrect dates.
}
\cvitem{\href{https://github.com/rzhou10/Music-Search-and-Recommendation}{\textbf{Music Search and Recommendation}}}{
    A \textbf{Node.js} web app to find songs based on user defined query (title, artist, etc).
}
\cvitem{\href{https://github.com/rzhou10/Boss-Fight}{\textbf{Boss Fight}}}{
    A \textbf{Java} turn based game where one fights 7 bosses in a row. 
}

\section{Skills}
\cvitem{Programming Languages}{C\#, CSS, HTML, JavaScript, Python, SQL}
\cvitem{Libraries/Frameworks}{ASP.NET, Bootstrap, Express.js, Node.js, React.js, Vue.js}
\cvitem{Miscellanous Tools}{Cypress, Git, GitHub, Google Cloud Function (GCP), JSON, Jira, MongoDB, MySQL, VSCode, WebStorm}

\end{document}