\documentclass[10pt,letterpaper]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[scale=0.7,margin=0.5in]{geometry}
\usepackage{lmodern}

\name{Renjie}{Zhou}
\email{rzhou10@gmail.com}
\phone[mobile]{609-933-0310}
\address{}{Hoboken, NJ, 07030}
\homepage{https://blackmartentrace.com/}
\social[linkedin]{rzhou10}
\social[github]{rzhou10}

\vspace*{-15mm}

\begin{document}

\makecvtitle

%change width of \cventry year
\sethintscolumntowidth{mmm yyyy -- mmm y}

\section{Education}
\cventry{Aug 2014 - May 2019}{B.E. Computer Engineering}{Stevens Institute of Technology}{Hoboken, NJ}{}{
	\begin{itemize}
        \item IEEE student branch
        \item Stevens Computer Science Club (SCSC)
        \item Society of Asian Scientists and Engineers (SASE)
        \item Filipino Association of Stevens Tech (FAST)
	\end{itemize}
}

\section{Work Experience}

\cventry{Sept 2022 - Present}{Software Engineer}{Shoppable\textregistered}{New York, NY}{}{
    \begin{itemize}
        \item Redesigned the dashboard to handle Google Analytics 4 and reduce unnecessary information
        \item Refactored projects to remove unused npm packages and clean up code base
        \item Redesigned the Shoppable\textregistered Ad Experience to use Handlebars.js to reduce load times and to integrate the DTC checkout experience
        \item Created an endpoint to allow users to programmatically conduct checkouts for greater flexibility in integrating with Shoppable
\end{itemize}}
\cventry{Jul 2021 - Sept 2022}{Junior Software Engineer}{Shoppable\textregistered}{New York, NY}{}{
    \begin{itemize}
        \item Created builders for DTC and InstantShop to let users customize the look and layouts.
        \item Created an interface to allow the user to change details about specific products
        \item Refactored the code base for DTC to follow better React practices, resulting in a better performance and smaller code base
        \item Designed and built an admin interface to allow internal employees to manage information about merchants and customers
\end{itemize}}

\cventry{Jul 2019 - May 2021}{Software Developer}{Sphere Technology Solutions}{Hoboken, NJ}{}{
    \begin{itemize}
        \item Fixed UI bugs on Sphereboard to fix broken functionality, and changed stored procedure logic to return accurate information.
        \item Added new features to improve usability, such as the violation work table and the suspected admin finder.
        \item Modified the Connectors and Ingestor to collect/process additional information about files and folders, and to improve stability.
\end{itemize}
}
\cventry{Jun 2018 - Aug 2018}{Intern}{MedAZ.net}{West Windsor, NJ}{}{
    \begin{itemize}
        \item Built RESTful APIs to dynamically retrieve and update website data.  
        \item Utilized OATH authentication to allow password-less login via external services such as Facebook or Google.
        \item Sped up database access by replacing the previous Entity Framework with the faster Dapper ORM library.
\end{itemize}}

\cventry{Jul 2017 - Aug 2017}{Developer Intern}{MedAZ.net}{Princeton Junction, NJ}{}{
    \begin{itemize}
        \item Refactored the MaiEDEN web app to improve user accessibility and usability.
        \item Changed the color and position of buttons.
        \item Added functionalities such as a contact form, and a new service page.
\end{itemize}}

\cventry{Nov 2015 - May 2018}{Publication Assistant}{Stevens Physics Department}{Hoboken, NJ}{}{
    \begin{itemize}
    \item Transcribed supervisor's research papers in LaTeX in preparation for publication.
    \item Retrieved articles from journal publications for supervisor's collection.
    \item Aided the supervisor with personal tasks, such as delivering items between his apartment and his office.
\end{itemize}}

\section{Projects}
\cvitem{\href{https://github.com/chloequinto/SSW_555_Project}{\textbf{GEDCOM (genealogical data) parser}}}{
    A \textbf{Python} GEDCOM file parser to display information about a family tree, such as living people, and catch errors, such as incorrect dates.
}
\cvitem{\href{https://github.com/rzhou10/Music-Search-and-Recommendation}{\textbf{Music Search and Recommendation}}}{
    A \textbf{JavaScript} web app to find songs based on user defined query (title, artist, etc).
}
\cvitem{\href{https://github.com/rzhou10/Boss-Fight}{\textbf{Boss Fight}}}{
    A \textbf{Java} turn based game where one fights 7 bosses in a row. 
}

\section{Skills}
\cvitem{Languages}{CSS, HTML, JavaScript, Python}
\cvitem{Tools/Technology}{Git, Google Cloud, Jira, MongoDb, LaTeX, Ubuntu, Visual Studio Code, Webstorm IDE}
\cvitem{Web Tools}{Bootstrap, Express.js, Node.js, React.js, Vue.js}

\end{document}